MRPSO: MapReduce Particle Swarm Optimization

### 2009-01-05 crystallography/paper.tex
removed some great features so paper.tex will actually compile

\usepackage{cite}
\usepackage{graphicx}
\usepackage{psfrag}
\usepackage{subfigure}
\usepackage{listings}
\usepackage{amsmath,amssymb}
\usepackage{array}
\usepackage{algorithm}

@@

@@

% Names of things
\providecommand{\RadiusSEPSOLong}{Contracting Radius SEPSO}
\providecommand{\DistanceSEPSOLong}{Contracting Radius, Increasing Bounce SEPSO}
\providecommand{\RadiusSEPSO}{CRS}
\providecommand{\DistanceSEPSO}{CRIBS}

@@

TODO: **Matt, you probably want to put this in your own words, but if we
really run out of time, you don't really have to.**

@@

Each particle's position and velocity are initialized to random values based
on a function-specific feasible region.  During each iteration of constricted
PSO, the following equations update a particle's position $\ppos$ and velocity
$\pvel$ with respect to personal best $\pbest$ and global best $\gbest$:
\begin{align}
\label{eq:velupdate}
    \pvel_{t+1} &=
        \constriction \left[ \pvel_t + 
            \coeff_1\URand()\otimes(\pbest - \ppos_{t}) +
            \coeff_2\URand()\otimes(\gbest - \ppos_{t})
        \right] \\
\label{eq:posupdate}
    \ppos_{t+1} &= \ppos_t + \pvel_{t+1}
\end{align}
where \(\coeff_1 = \coeff_2 = 2.05\), \(\URand()\) is a vector of samples
drawn from a standard uniform distribution, and \( \otimes \) represents
element-wise multiplication.  The constriction constant \( \constriction \)
is:
\begin{align}
    \notag
    \constriction &= \frac{2 \kappa}{|2 - \coeff - \sqrt{\coeff^2 - 4\coeff}|}
\end{align}
where
$\coeff = \coeff_1 + \coeff_2$ and $\kappa$ is usually
$1.0$.~\citep{clerc-tec02}

@@

TODO: **Matt, you probably want to put this in your own words, but if we
really run out of time, you don't really have to.  This should also be trimmed
down.**

@@

The following notation and example are based on the original
presentation~\citep{dean-osdi04}.

>>>>

\usepackage{graphicx}
\usepackage{psfrag}
\usepackage{subfigure}
\usepackage{listings}
\usepackage{amsmath,amssymb}
\usepackage{array}
\usepackage{algorithm}

@@

% AML bibliography references
\newcommand{\bib}[1]{../../papers/#1}

@@

@@

TODO: Matt, you probably want to put this in your own words, but if we
really run out of time, you don't really have to.

@@

Each particle's position and velocity are initialized to random values based
on a function-specific feasible region.  During each iteration of constricted
PSO, the following equations update a particle's position $\ppos$ and velocity
$\pvel$ with respect to personal best $\pbest$ and global best $\gbest$:
\begin{align}
\label{eq:velupdate}
    \pvel_{t+1} &=
        \constriction \left[ \pvel_t + 
            \coeff_1\URand()\otimes(\pbest - \ppos_{t}) +
            \coeff_2\URand()\otimes(\gbest - \ppos_{t})
        \right] \\
\label{eq:posupdate}
    \ppos_{t+1} &= \ppos_t + \pvel_{t+1}
\end{align}
where $\coeff_1 = \coeff_2 = 2.05$, $\URand()$ is a vector of samples
drawn from a standard uniform distribution, and $\otimes$ represents
element-wise multiplication.  The constriction constant $\constriction$
is:
\begin{align}
    \notag
    \constriction &= \frac{2 \kappa}{|2 - \coeff - \sqrt{\coeff^2 - 4\coeff}|}
\end{align}
where
$\coeff = \coeff_1 + \coeff_2$ and $\kappa$ is usually
$1.0$~\cite{clerc-tec02}.

@@

TODO: Matt, you probably want to put this in your own words, but if we
really run out of time, you don't really have to.  This should also be trimmed
down.

@@

The following notation and example are based on the original
presentation~\cite{dean-osdi04}.
